Risk Factors and Treatment of Refractory Anaphylaxis - a review of case reports

### 2018-02-23 analysis/paper/paper.Rmd
references corrected

---
title: 'Risk Factors and Treatment of Refractory Anaphylaxis - a review of case reports'
author:
  - Wojciech Francuzik
  - Sabine Dölle
  - Margitta Worm, MD
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: 
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../templates/templateNumberedSections.docx"
bibliography: references.bib
csl: erci.csl
abstract: |
  **Introduction:** Patients experiencing anaphylaxis who do not recover after the treatment with intramuscular adrenaline are regarded to suffer from refractory anaphylaxis. The incidence of refractory anaphylaxis is estimated to range between 3--5% of anaphylaxis cases. The risk factors for refractory anaphylaxis are unknown.

>>>>

---
title: 'Risk Factors and Treatment of Refractory Anaphylaxis - a review of case reports'
author:
  - Wojciech Francuzik
  - Sabine Dölle
  - Margitta Worm, MD
date: "`r format(Sys.time(), '%d.%m.%Y')`"
output: 
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../templates/templateNumberedSections.docx"
bibliography: references.bib
csl: expert-review-of-clinical-immunology.csl
abstract: |
  **Introduction:** Patients experiencing anaphylaxis who do not recover after the treatment with intramuscular adrenaline are regarded to suffer from refractory anaphylaxis. The incidence of refractory anaphylaxis is estimated to range between 3--5% of anaphylaxis cases. The risk factors for refractory anaphylaxis are unknown.
